### 2020-02-06 thesis/paper.tex
citations & sections

@@

\section{Other Methods}
\subsection{Hungarians Method}

@@

As the data may still contain unwanted dimensions after loading cleanup may need to be done. To reduce the dimensionality the simplest method is to select the ``Dim. Remover'' tool in the top right and define the index of the dimension to be removed. As more sophisticated methods PCA and t-SNE [CITATION] are also available. PCA calculates the principal components of the data and projects it onto the $k$ strongest ones leaving us with $k$ dimensions. $k$ can easily be defined in the settings of PCA by filling in the dimensions field, as seen in Figure \ref{fig:loaded-data}. t-SNE works similarly to PCA, has more options though and even a parallel implementation. For more information on those methods see Section [REFERENCE].

>>>>

\subsection{k-Means}

\subsection{DBSCAN}

@@

\subsection{Co-association Matrix based Consensus}

\subsubsection{Lifetime Criterion}

\section{Other Methods}
\subsection{Dimensionality Reduction}\label{sec:dim_reduction}
PCA \cite{pca}

 t-SNE \cite{Maaten2008VisualizingDU}

\subsection{Hungarians Method}

@@

As the data may still contain unwanted dimensions after loading cleanup may need to be done. To reduce the dimensionality the simplest method is to select the ``Dim. Remover'' tool in the top right and define the index of the dimension to be removed. As more sophisticated methods PCA \cite{pca} and t-SNE \cite{Maaten2008VisualizingDU} are also available. PCA calculates the principal components of the data and projects it onto the $k$ strongest ones leaving us with $k$ dimensions. $k$ can easily be defined in the settings of PCA by filling in the dimensions field, as seen in Figure \ref{fig:loaded-data}. t-SNE works similarly to PCA, has more options though and even a parallel implementation. For more information on those methods see Section \ref{sec:dim_reduction}.
